---
title: "MAMA Assignment Session 1"
author: "Your name goes here"
date: "`r Sys.Date()`"
output:
  html_document:
    highlight: zenburn
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(plotly)
library(lubridate)
library(fivethirtyeight)
library(here)
```


> In all of these exercises, you may find useful the material on [visualising data](http://telapps.london.edu/analytics_with_R/visualise_data.html). Also, please submit your work without any of the text I have written-- just your code, plots, and explanations/stories.

# Task 1: Where Do People Drink The Most Beer, Wine And Spirits?

Back in 2014, [fivethiryeight.com](https://fivethirtyeight.com/features/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/) published an article on alchohol consumption in different countries. The data `drinks` is available as part of the `fivethirtyeight` package. Make sure you have installed the `fivethirtyeight` package before proceeding.


```{r, load_alcohol_data}
library(fivethirtyeight)
data(drinks)

# or download directly
# alcohol_direct <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv")

```


Make a plot that shows the top 25 beer consuming countries

```{r beer_plot}
# YOUR CODE GOES HERE


```

Make a plot that shows the top 25 wine consuming countries

```{r wine_plot}

# YOUR CODE GOES HERE


```

Finally, make a plot that shows the top 25 spirit consuming countries
```{r spirit_plot}
# YOUR CODE GOES HERE

```

What can you infer from these plots? Don't just explain what's in the graph, but speculate or tell a short story (1-2 paragraphs max).

> TYPE YOUR ANSWER AFTER (AND OUTSIDE!) THIS BLOCKQUOTE.



# All done!

Knit the completed R Markdown file as an HTML document (use the "Knit" button at the top of the script editor window) and upload it to Canvas.

# Details

- Who did you collaborate with: TYPE NAMES HERE
- Approximately how much time did you spend on this problem set: ANSWER HERE
- What, if anything, gave you the most trouble: ANSWER HERE


# Rubric

Check minus (1/5): Displays minimal effort. Doesn't complete all components. Code is poorly written and not documented. Uses the same type of plot for each graph, or doesn't use plots appropriate for the variables being analyzed. 

Check (3/5): Solid effort. Hits all the elements. No clear mistakes. Easy to follow (both the code and the output). 

Check plus (5/5): Finished all components of the assignment correctly and addressed both challenges. Code is well-documented (both self-documented and with additional comments as necessary). Used tidyverse, instead of base R. Graphs and tables are properly labelled. Analysis is clear and easy to follow, either because graphs are labeled clearly or you've written additional text to describe how you interpret the output.




