---
title: "Challenge 2"
output: html_document
---

``````{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest) # to scrape wikipedia page
```


```{r}
url <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2021_German_federal_election"
# https://www.economist.com/graphic-detail/who-will-succeed-angela-merkel
# https://www.theguardian.com/world/2021/jun/21/german-election-poll-tracker-who-will-be-the-next-chancellor


# get tables that exist on wikipedia page 
tables <- url %>% 
  read_html() %>% 
  html_nodes(css="table")


# parse HTML tables into a dataframe called polls 
# Use purr::map() to create a list of all tables in URL
polls <- map(tables, . %>% 
             html_table(fill=TRUE)%>% 
             janitor::clean_names())


# list of opinion polls
german_election_polls <- polls[[1]] %>% # the first table on the page contains the list of all opinions polls
  slice(2:(n()-1)) %>%  # drop the first row, as it contains again the variable names and last row that contains 2017 results
  mutate(
         # polls are shown to run from-to, e.g. 9-13 Aug 2021. We keep the last date, 13 Aug here, as the poll date
         # and we extract it by picking the last 11 characters from that field
         end_date = str_sub(fieldwork_date, -11),
         
         # end_date is still a string, so we convert it into a date object using lubridate::dmy()
         end_date = dmy(end_date),
         
         # we also get the month and week number from the date, if we want to do analysis by month- week, etc.
         month = month(end_date),
         week = isoweek(end_date)
         )
```


```{r}
nrow(german_election_polls)

#Removing duplicate values
german_election_polls <- german_election_polls[!duplicated(german_election_polls), ]

nrow(german_election_polls)
```


```{r}
#Setting colors for different political parties
col_union = "Black"
col_spd = "red3"
col_afd = "blue3"
col_fdp = "Orange"
col_linke = "purple3"
col_grune = "green3"

colors <- c("Sepal Width" = "blue", "Petal Length" = "red", "Petal Width" = "orange")
```


```{r}
#Calculating rolling average for different political parties

german_election_polls_avg <- german_election_polls %>% 
  mutate(
    union_avg = rollmean(union, 14, align="left", fill = NA),
    spd_avg = rollmean(spd, 14, align="left", fill = NA),
    afd_avg = rollmean(af_d, 14, align="left", fill = NA),
    fdp_avg = rollmean(fdp, 14, align="left", fill = NA),
    linke_avg = rollmean(linke, 14, align="left", fill = NA),
    grune_avg = rollmean(grune, 14, align="left", fill = NA)
    )
```



```{r}
#Plotting the graph

german_election_polls_avg %>% 
  ggplot +
  
  #Union
  geom_point(aes(x=end_date,y=union),color=col_union, alpha=0.5)+
  geom_line(aes(x=end_date,y=union_avg),
            se=FALSE,color=col_union,size=1.1, alpha=0.6)+
  #spd
  geom_point(aes(x=end_date,y=spd),color=col_spd, alpha=0.5)+
  geom_line(aes(x=end_date,y=spd_avg),
            se=FALSE,color=col_spd,size=1.1, alpha=0.6)+
  #af_d
  geom_point(aes(x=end_date,y=af_d),color=col_afd, alpha=0.5)+
  geom_line(aes(x=end_date,y=afd_avg),
            se=FALSE,color=col_afd,size=1.1, alpha=0.6)+
  #fdp
  geom_point(aes(x=end_date,y=fdp),color=col_fdp, alpha=0.5)+
  geom_line(aes(x=end_date,y=fdp_avg),
            se=FALSE,color=col_fdp,size=1.1, alpha=0.6)+
  #linke
  geom_point(aes(x=end_date,y=linke),color=col_linke, alpha=0.5)+
  geom_line(aes(x=end_date,y=linke_avg),
            se=FALSE,color=col_linke,size=1.1, alpha=0.6)+
  #grune
  geom_point(aes(x=end_date,y=grune),color=col_grune, alpha=0.5)+
  geom_line(aes(x=end_date,y=grune_avg),
            se=FALSE,color=col_grune,size=1.1, alpha=0.6)+
  
  #Setting x and y axes labels to be null
  labs(x="", y="") +
  
  #Date labels for x-axis
  scale_x_date(date_minor_breaks = "1 months", 
               date_labels = "%b %Y") +
  
  #Percentage labels for y-axis
  scale_y_continuous(breaks = c(5, 15, 25, 35, 45),
                     labels = function(x) paste0(x, "%")) +
  
  #Setting black and white theme, and removing grid lines
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  
  #Plotting horizontal lines 
  geom_hline(aes(yintercept = 5), linetype="dashed", alpha=0.2) +
  geom_hline(aes(yintercept = 15), linetype="dashed", alpha=0.2) +
  geom_hline(aes(yintercept = 25), linetype="dashed", alpha=0.2) +
  geom_hline(aes(yintercept = 35), linetype="dashed", alpha=0.2)+
  
  #Annotate
  scale_color_manual(values = colors)

```




